\documentclass[11pt,a4paper]{article}
\usepackage[a4paper,margin=1in]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{hyperref}
\usepackage{paracol}
\usepackage{xcolor}
\usepackage{parskip}
\usepackage{fontawesome5}
\usepackage{ragged2e}

\definecolor{sectioncolor}{RGB}{30,30,30}
\titleformat{\section}{\large\bfseries\color{sectioncolor}\vspace{0.5em}}{}{0em}{}
\titleformat{\subsection}[runin]{\bfseries}{}{0em}{}[\ ---]
\renewcommand{\familydefault}{\sfdefault}

\hypersetup{
    colorlinks=true,
    linkcolor=sectioncolor,
    filecolor=sectioncolor,
    urlcolor=sectioncolor,
}

% Adjust column ratio for harmony
\setcolumnratio{0.38,0.62}

% Reduce vertical space between items for compactness
\setlist[itemize]{itemsep=2pt, topsep=2pt, leftmargin=*}

\begin{document}

% Header spanning both columns
\begin{center}
    {\LARGE \textbf{Waberi Daher}} \\[2pt]
    Brussels, Belgium ~|~ +32 485 76 88 17 ~|~ \href{mailto:waberryd@gmail.com}{waberryd@gmail.com} \\[1pt]
    \href{https://www.linkedin.com/in/waberi-daher}{LinkedIn} ~|~ \href{https://github.com/berrythewa}{GitHub}
\end{center}
\vspace{0.5em}

% --- About Me (full width) ---
\section*{About Me}
\justifying
Versatile and hands-on fullstack developer with a strong focus on \textbf{system reliability}, \textbf{data control}, and \textbf{cross-platform tools}. I care deeply about clarity in code and maintainability in systems. Currently building a native clipboard manager from the ground up with Go, Rust, and Tauri.

\vspace{1.5em}

% --- Two columns: Skills | Experience ---
\begin{paracol}{2}

% Left column: Skills
\section*{Skills}
\begin{itemize}
  \item \textbf{Languages:} Python, JavaScript, TypeScript, Go, Java, C/C++
  \item \textbf{Frameworks:} React, React Native, Next.js, Express.js, NestJS, Django, FastAPI
  \item \textbf{Databases:} PostgreSQL, MySQL, MongoDB, Prisma ORM
  \item \textbf{Infra:} Docker, GitHub Actions, CI/CD pipelines
  \item \textbf{Learning:} Kubernetes, Terraform
  \item \textbf{Concepts:} REST, GraphQL, tRPC, security, privacy, fullstack systems
\end{itemize}

\switchcolumn

% Right column: Experience
\section*{Experience}
\subsection{Leanity \hfill Jan 2024 -- Jun 2024}
\textit{Fullstack Developer (Internship)} \\
\textbf{Tech:} TypeScript, Next.js, Prisma, GraphQL, tRPC, PostgreSQL
\begin{itemize}
    \item Built modern web apps with type-safe frontend/backend communication.
    \item Designed GraphQL APIs and managed database schemas with Prisma.
    \item Contributed to Agile feature delivery cycles.
\end{itemize}

\subsection{Efficy CRM \hfill Sep 2022 -- Oct 2023}
\textit{Fullstack Developer} \\
\textbf{Tech:} JavaScript, SQL, jQuery, REST, SOAP
\begin{itemize}
    \item Integrated and maintained REST and SOAP APIs.
    \item Handled structured data imports and backend scripts.
    \item Contributed to custom CRM workflows.
\end{itemize}

\subsection{Deloitte (Bruxelles Fiscalité) \hfill Jun 2021 -- Dec 2021}
\textit{Fullstack Developer} \\
\textbf{Tech:} Java, Scala, React Native, Gatling, SSR Java CMS
\begin{itemize}
    \item Contributed to SSR website and custom Java CMS.
    \item Developed mobile components in React Native.
    \item Conducted performance/load testing with Gatling.
\end{itemize}

\subsection{Chatbot Plus \hfill Jul 2020 -- Nov 2020}
\textit{Fullstack JavaScript Intern} \\
\textbf{Tech:} Express.js, React, MongoDB
\begin{itemize}
    \item Built backend services with Express.js.
    \item Created React dashboards for analytics.
    \item Implemented data visualizations from user metrics.
\end{itemize}

\end{paracol}

% --- New Page ---
\newpage

% --- Two columns: (Languages, Interests) | (Selected Project, Education) ---
\begin{paracol}{2}

% Left column: Languages, Interests
\section*{Languages}
\begin{itemize}
  \item \textbf{French:} Native
  \item \textbf{English:} Fluent (UK immersion)
  \item \textbf{Somali:} Native
\end{itemize}

\vspace{1em}

\section*{Interests}
\begin{itemize}
  \item Free and open-source software
  \item Network security and system monitoring
  \item Custom tooling and automation
  \item Jazz and underground music events
  \item Geopolitics, tech history, and philosophy
\end{itemize}

\switchcolumn

% Right column: Selected Project, Education
\section*{Selected Project}
\subsection{Clipboard Manager (MVP In Progress)}
\textbf{Tech:} Golang, Rust, Tauri, MQTT, WebSockets
\begin{itemize}
    \item Native cross-platform clipboard manager with privacy-first sync.
    \item Local-first architecture with secret handling and extensibility.
    \item Built from scratch for speed and control.
\end{itemize}

\vspace{1em}

\section*{Education}
\subsection{Université Libre de Bruxelles (ULB) \hfill 2024 -- Present}
Bachelor's in Mathematics (ongoing) \\
Currently enrolled; preparing for core exams in algebra, analysis, and discrete mathematics.

\subsection{42 Brussels / School 19 \hfill 2018 -- 2020}
Peer-to-peer software engineering program focused on system-level and project-based learning.

\subsection{Université Libre de Bruxelles (ULB) \hfill 2013 -- 2016 (incomplete)}
Bachelor's in Computer Science.

\subsection{Brasshouse Language School, Birmingham \hfill 2012}
English language immersion course.

\subsection{CESS – Collège Sainte-Marie, Mouscron \hfill 2007 -- 2011}
STEM-focused Belgian secondary diploma.

\end{paracol}

\end{document}
